Compilation through interpretation

### 2023-05-23 Papers/FEDCIS-2023/cm1.tex
fixed article

\author{
	\IEEEauthorblockN{Adam Grabski}
	\IEEEauthorblockA{0000-0002-6283-8461\\
		Warsaw Univeristy of Technology\\
		in Warsaw\\
		ul.\ Nowowiejska 15/19, 00-665 Warsaw, Poland\\
		Email: adam.grabski@stud.pw.edu.pl}
	\and
	\IEEEauthorblockN{Ilona Bluemke}
	\IEEEauthorblockA{0000-0002-2894-5976\\
		Warsaw Univeristy of Technology\\
		in Warsaw\\
		ul.\ Nowowiejska 15/19, 00-665 Warsaw, Poland\\
		Email: Ilona.Bluemke@pw.edu.pl}
}

>>>>

\author{
	\IEEEauthorblockN{Adam Grabski}
	\IEEEauthorblockA{0000-0002-6283-8461\\
		Warsaw Univeristy of Technology\\
		in Warsaw\\
		ul.\ Nowowiejska 15/19, 00-665 Warsaw, Poland\\
		Email: adam.gr@outlook.com}
	\and
	\IEEEauthorblockN{Ilona Bluemke}
	\IEEEauthorblockA{0000-0002-2894-5976\\
		Warsaw Univeristy of Technology\\
		in Warsaw\\
		ul.\ Nowowiejska 15/19, 00-665 Warsaw, Poland\\
		Email: Ilona.Bluemke@pw.edu.pl}
}
